\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex
clean up prescreening appendix

{\color {red}
\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We show the responses from the participants that we chose.

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 81\% (13/16) \\ %13/16
Proxy services & 69\% (11/16)\\ %11/16
Phishing & 63\% (10/16)\\ %10/16
SSL & 63\% (10/16)\\%10/16
X.511 certificates & 25\% (4/16)\\ %4/16
Tor & 50\% (8/16)\\ %8/16
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}

We suspect that participants answered dishonestly in hopes of appearing more technically fluent. We know this because some reported that they were familiar a term that did not exist (x.511 certificates). We inserted this fictional term specifically to detect this.

\begin{table*}[h]
\centering
\begin{tabular}{l r r r r r r}
& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Missing}\\
& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily} & \multicolumn{1}{r}{answer}\\
\noalign{\hrule}
HTTPS on web pages				& 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 25\% (4/16) & 56\% (9/16) & 0\% (0/16) \\
Proxies or censorship circumvention tools & 50\% (8/16) & 13\% (2/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 13\% (2/16) \\
Virtual private networks (VPNs) 		& 44\% (7/16) & 31\% (5/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
File or disk encryption 				& 50\% (8/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 25\% (4/16) & 1\% (1/16) \\
Anonymity systems (e.g. Tor) 			& 63\% (10/16) & 13\% (2/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) \\
Email encryption (e.g. PGP) 			& 50\% (8/16) & 19\% (3/16) & 19\% (3/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
Instant messaging encryption 			& 44\% (7/16) & 25\% (4/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 1\% (1/16) \\
Voice communication encryption 		& 81\% (13/16) & 1\% (1/16) & 1\% (1/16) & 0\% (0/16) & 0\% (0/16) &1\% (1/16)\\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-software}
\end{table*}

We assume that self-reported use is the upper bound of how many participants have used these security tools.
}

>>>>

\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We did {\it not} use this information to influence the experimental procedure (i.e. use this to pick their environment). We show their responses:

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 81\% (13/16) \\ %13/16
Proxy services & 69\% (11/16)\\ %11/16
Phishing & 63\% (10/16)\\ %10/16
SSL & 63\% (10/16)\\%10/16
X.511 certificates & 25\% (4/16)\\ %4/16
Tor & 50\% (8/16)\\ %8/16
\end{tabular}
\caption{
Formative users' self-reported familiarity with various security terms. 
}
\label{table:selfreported-tech}
\end{table}

Table~\ref{table:selfreported-software} lists their self-reported familiarity with various security concepts. Some reported that they were familiar a term that did not exist (x.511 certificates). We inserted this fictional term specifically to detect this. We suspect that participants answered dishonestly in hopes of appearing more technically fluent.

\begin{table*}[h]
\centering
\begin{tabular}{l r r r r r r}
& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Missing}\\
& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily} & \multicolumn{1}{r}{answer}\\
\noalign{\hrule}
HTTPS on web pages				& 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 25\% (4/16) & 56\% (9/16) & 0\% (0/16) \\
Proxies or censorship circumvention tools & 50\% (8/16) & 13\% (2/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 13\% (2/16) \\
Virtual private networks (VPNs) 		& 44\% (7/16) & 31\% (5/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
File or disk encryption 				& 50\% (8/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 25\% (4/16) & 1\% (1/16) \\
Anonymity systems (e.g. Tor) 			& 63\% (10/16) & 13\% (2/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) \\
Email encryption (e.g. PGP) 			& 50\% (8/16) & 19\% (3/16) & 19\% (3/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
Instant messaging encryption 			& 44\% (7/16) & 25\% (4/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 1\% (1/16) \\
Voice communication encryption 		& 81\% (13/16) & 1\% (1/16) & 1\% (1/16) & 0\% (0/16) & 0\% (0/16) &1\% (1/16)\\
\end{tabular}
\caption{
Formative users' self-reported use of various security software. 
}
\label{table:selfreported-software}
\end{table*}

Table~\ref{table:selfreported-software} lists their self-reported use of security software. Similarly to self-reported familiarity, we assume that participants answered to appear more technically fluent. We assumed that this self-reported use of security tools is an approximate upper bound of how many have actually used these security tools.
